Analysis of the properties of probabilistic models in learning problems with an expert\thanks{The reported study was funded by RFBR according to the research projects 20-37-90050, 19-07-01155 and NTI project 13/1251/2018.}

### 2020-12-30 paper/Bazarova2020Springer/BliendedManuscript.tex
last version

\title{Analysis of the properties of probabilistic models in learning problems with an expert\thanks{Grants or other notes
about the article that should go on the front page should be
placed here. General acknowledgments should be placed at the end of the article.}
}
\subtitle{}

@@

\author{Andrey V. Grabovoy        \and
            Alexandra I. Bazarova  \and
            Vadim V. Strijov
}

%\authorrunning{Short form of author list} % if too long for running head
\institute{
            Andrey V. Grabovoy\at Moscow Institute of Physics and Technology\\
              9 Institutskiy per., Dolgoprudny, Moscow Region, 141701, Russian Federation \\
              \email{grabovoy.av@phystech.edu}
           \and
           Alexandra I. Bazarova\at Moscow Institute of Physics and Technology\\
              9 Institutskiy per., Dolgoprudny, Moscow Region, 141701, Russian Federation \\
              \email{bazarova.ai@phystech.edu}
           \and
           Vadim V. Strijov \at Moscow Institute of Physics and Technology\\
              9 Institutskiy per., Dolgoprudny, Moscow Region, 141701, Russian Federation \\
              \email{strijov@phystech.edu}
}

@@

>>>>

\title{Analysis of the properties of probabilistic models in learning problems with an expert\thanks{The reported study was funded by RFBR according to the research projects 20-37-90050, 19-07-01155 and NTI project 13/1251/2018.}
}
\subtitle{}

@@

\author{}

%\author{Andrey V. Grabovoy        \and
%            Alexandra I. Bazarova  \and
%            Vadim V. Strijov
%}

\institute{}

%\authorrunning{Short form of author list} % if too long for running head
%\institute{
%            Andrey V. Grabovoy\at Moscow Institute of Physics and Technology\\
%              9 Institutskiy per., Dolgoprudny, Moscow Region, 141701, Russian Federation \\
%              \email{grabovoy.av@phystech.edu}
%           \and
%           Alexandra I. Bazarova\at Moscow Institute of Physics and Technology\\
%              9 Institutskiy per., Dolgoprudny, Moscow Region, 141701, Russian Federation \\
 %             \email{bazarova.ai@phystech.edu}
 %          \and
 %          Vadim V. Strijov \at Moscow Institute of Physics and Technology\\
 %             9 Institutskiy per., Dolgoprudny, Moscow Region, 141701, Russian Federation \\
 %             \email{strijov@phystech.edu}
%}

@@

\section{Acknowledgments}
\label{sec:7}
The reported study was funded by RFBR according to the research projects 20-37-90050, 19-07-01155 and NTI project 13/1251/2018.
